Uranyl solvation by a three-dimensional reference interaction site model

### 2015-04-17 doc/uo2_paper/uo2-II.tex
AM: inline bibliography

\bibliography{bibliography}

>>>>

% %\bibliography{bibliography}
\begin{thebibliography}{96}

\bibitem{book:Morss06}
Morss,~L.~R.; Edelstein,~N.~M.; Fuger,~J. \emph{The Chemistry of the Actinide
  and Transactinide Elements}, 3rd ed.; Springer: Netherlands, 2006; Vol.~1; pp
  253--697.
\bibitem{book:Grenthe92}
Grenthe,~I.; Fuger,~J.; Konings,~R.; Lemire,~R.; Muller,~A.; Nguyen-Trung,~C.;
  Wanner,~H. \emph{Chemical Thermodynamics of Uranium}; North-Holland:
  Amsterdam, 1992.
\bibitem{Silva95}
Silva,~R.; Nitsche,~H. Actinide Environmental Chemistry. \emph{Radiochim. Acta}
  \textbf{1995}, \emph{70}, 377--396.
\bibitem{Tomasi05}
Tomasi,~J.; Mennucci,~B.; Cammi,~R. Quantum Mechanical Continuum Solvation
  Models. \emph{Chem. Rev.} \textbf{2005}, \emph{105}, 2999--3094.
\bibitem{Fuchs02}
Fuchs,~M.; Shor,~A.~M.; R\"{o}sch,~N. The Hydration of the Uranyl Dication.
  {I}ncorporation of Solvent Effects in Parallel Density Functional
  Calculations with the Program \textsc{{P}ara{G}auss}. \emph{Int. J. Quantum
  Chem.} \textbf{2002}, \emph{86}, 487--501.
\bibitem{Klamt95}
Klamt,~A. Conductor-like Screening Model for Real Solvents: A New Approach to
  the Quantitative Calculation of Solvation Phenomena. \emph{J. Phys. Chem.}
  \textbf{1995}, \emph{99}, 2224--2235.
\bibitem{Moskaleva04}
Moskaleva,~L.~V.; Kr\"{u}ger,~S.; Sp\"{o}rl,~A.; R\"{o}sch,~N. Role of
  Solvation in the Reduction of the Uranyl Dication by Water: A Density
  Functional Study. \emph{Inorg. Chem.} \textbf{2004}, \emph{43},
  4080--4090.
\bibitem{Cao05}
Cao,~Z.; Balasubramanian,~K. Theoretical Studies of
  {UO$_{2}($H$_{2}$O$)_{n}^{2+}$}, {NpO$_{2}($H$_{2}$O$)_{n}^{+}$}, and
  {PuO$_{2}($H$_{2}$O$)_{n}^{2+}$} Complexes ($n=4-6$) in Aqueous Solution and
  Gas Phase. \emph{J. Chem. Phys.} \textbf{2005}, \emph{123}, 114309.
\bibitem{Shamov05}
Shamov,~G.~A.; Schreckenbach,~G. Density Functional Studies of Actinyl Aquo
  Complexes Studied Using Small-Core Effective Core Potentials and a Scalar
  Four-Component Relativistic Method. \emph{J. Phys. Chem. A} \textbf{2005},
  \emph{109}, 10961--10974.
\bibitem{Gutowski06}
Gutowski,~K.~E.; Dixon,~D.~A. Predicting the Energy of the Water Exchange
  Reaction and Free Energy of Solvation for the Uranyl Ion in Aqueous Solution.
  \emph{J. Phys. Chem. A} \textbf{2006}, \emph{110}, 8840--8856.
\bibitem{Guilbaud93}
Guilbaud,~P.; Wipff,~G. Hydration of Uranyl ({UO$_2^{2+}$}) Cation and its
  Nitrate Ion and 18-crown-6 Adducts Studied by Molecular Dynamics Simulations.
  \emph{J. Phys. Chem.} \textbf{1993}, \emph{97}, 5685--5692.
\bibitem{Guilbaud96}
Guilbaud,~P.; Wipff,~G. Force Field Representation of the {UO}$_2^{2+}$ Cation
  from Free Energy {MD} Simulations in Water. {T}ests on its 18-crown-6 and
  {NO}$_3$- Adducts, and on its calix[6]arene6- and {CMPO} Complexes. \emph{J.
  Mol. Struct.: THEOCHEM} \textbf{1996}, \emph{366}, 55--63.
\bibitem{Rai12}
Rai,~N.; Tiwari,~S.~P.; Maginn,~E.~J. Force Field Development for Actinyl Ions
  via Quantum Mechanical Calculations: An Approach to Account for Many Body
  Solvation Effects. \emph{J. Phys. Chem. B} \textbf{2012}, \emph{116},
  10885--10897.
\bibitem{Pomogaev13}
Pomogaev,~V.; Tiwari,~S.~P.; Rai,~N.; Goff,~G.~S.; Runde,~W.; Schneider,~W.~F.;
  Maginn,~E.~J. Development and Application of Effective Pairwise Potentials
  for {UO}$_2^{n+}$, {NpO}$_2^{n+}$, {PuO}$_2^{n+}$, and {AmO}$_2^{n+}$ ($n =
  1, 2$) Ions with Water. \emph{Phys. Chem. Chem. Phys.} \textbf{2013},
  \emph{15}, 15954--15963.
\bibitem{Kerisit13}
Kerisit,~S.; Liu,~C. Structure, Kinetics, and Thermodynamics of the Aqueous
  Uranyl({VI}) Cation. \emph{J. Phys. Chem. A} \textbf{2013}, \emph{117},
  6421--6432.
\bibitem{Tiwari14}
Tiwari,~S.~P.; Rai,~N.; Maginn,~E.~J. Dynamics of Actinyl Ions in Water: A
  Molecular Dynamics Simulation Study. \emph{Phys. Chem. Chem. Phys.}
  \textbf{2014}, \emph{16}, 8060--8069.
\bibitem[Griebel \latin{et~al.}(2007)Griebel, Knapek, and
  Zumbusch]{book:Griebel07}
Griebel,~M.; Knapek,~S.; Zumbusch,~G. \emph{Numerical Simulation in Molecular
  Dynamics: Numerics, Algorithms, Parallelization, Applications}; Springer:
  Berlin Heidelberg, 2007.
\bibitem{Gordon00}
Gordon,~M.~S.; Freitag,~M.~A.; Bandyopadhyay,~P.; Jensen,~J.~H.; Kairys,~V.;
  Stevens,~W.~J. The Effective Fragment Potential Method: A {QM}-Based {MM}
  Approach to Modeling Environmental Effects in Chemistry. \emph{J. Phys. Chem.
  A} \textbf{2000}, \emph{105}, 293--307.
\bibitem{hagberg05}
Hagberg,~D.; Karlstr\"{o}m,~G.; Roos,~B.~O.; Gagliardi,~L. The Coordination of
  Uranyl in Water: A Combined Quantum Chemical and Molecular Simulation Study.
  \emph{J. Am. Chem. Soc.} \textbf{2005}, \emph{127}, 14250--14256.
\bibitem[Frick \latin{et~al.}(2009)Frick, Hofer, Pribil, Randolf, and
  Rode]{Frick09}
Frick,~R.~J.; Hofer,~T.~S.; Pribil,~A.~B.; Randolf,~B.~R.; Rode,~B.~M.
  Structure and Dynamics of the {UO$_2^{2+}$} Ion in Aqueous Solution: An
  \textit{Ab Initio} {QMCF MD} Study. \emph{J. Phys. Chem. A} \textbf{2009},
  \emph{113}, 12496--12503.
\bibitem{Tirler13}
Tirler,~A.~O.; Weiss,~A. K.~H.; Hofer,~T.~S. A Comparative Quantum Mechanical
  Charge Field Study of Uranyl Mono- and Dicarbonate Species in Aqueous
  Solution. \emph{J. Phys. Chem. B} \textbf{2013}, \emph{117},
  16174--16187.
\bibitem{Buehl05}
B\"{u}hl,~M.; Diss,~R.; Wipff,~G. Coordination Environment of Aqueous
  Uranyl({VI}) Ion. \emph{J. Am. Chem. Soc.} \textbf{2005}, \emph{127},
  13506--13507.
\bibitem{Buehl06}
B\"{u}hl,~M.; Kabrede,~H.; Diss,~R.; Wipff,~G. Effect of Hydration on
  Coordination Properties of Uranyl({VI}) Complexes. {A} First-Principles
  Molecular Dynamics Study. \emph{J. Am. Chem. Soc.} \textbf{2006}, \emph{128},
  6357--6368.
\bibitem{Buehl11}
B\"{u}hl,~M.; Wipff,~G. Insights into Uranyl Chemistry from Molecular Dynamics
  Simulations. \emph{ChemPhysChem} \textbf{2011}, \emph{12}, 3095--3105.
\bibitem{Nichols08}
Nichols,~P.; Bylaska,~E.~J.; Schenter,~G.~K.; de~Jong,~W. Equatorial and Apical
  Solvent Shells of the {UO$_2^{2+}$} Ion. \emph{J. Chem. Phys.} \textbf{2008},
  \emph{128}, 124507.
\bibitem{book:Hirata03}
Hirata,~F. \emph{Molecular Theory of Solvation}; Kluwer Academic Publisher:
  Dordrecht, 2003.
\bibitem{book:Hansen06}
Hansen,~J.-P.; McDonald,~I.~R. \emph{Theory of Simple Liquids}, 3rd ed.;
  Academic Press: Burlington, 2006.
\bibitem{Chandler72}
Chandler,~D.; Andersen,~H.~C. Optimized Cluster Expansions for Classical
  Fluids. {II}. {T}heory of Molecular Liquids. \emph{J. Chem. Phys.}
  \textbf{1972}, \emph{57}, 1930--1937.
\bibitem{Hirata81}
Hirata,~F.; Rossky,~P.~J. An Extended {RISM} Equation for Molecular Polar
  Fluids. \emph{Chem. Phys. Lett.} \textbf{1981}, \emph{83}, 329--334.
\bibitem{Hirata82}
Hirata,~F.; Pettitt,~B.~M.; Rossky,~P.~J. Application of an Extended {RISM}
  Equation to Dipolar and Quadrupolar Fluids. \emph{J. Chem. Phys.}
  \textbf{1982}, \emph{77}, 509--520.
\bibitem{Kinoshita97}
Kinoshita,~M.; Hirata,~F. Analysis of Salt Effects on Solubility of Noble Gases
  in Water Using the Reference Interaction Site Model Theory. \emph{J. Chem.
  Phys.} \textbf{1997}, \emph{106}, 5202--5215.
\bibitem{Beglov95}
Beglov,~D.; Roux,~B. Numerical Solution of the Hypernetted Chain Equation for a
  Solute of Arbitrary Geometry in Three Dimensions. \emph{J. Chem. Phys.}
  \textbf{1995}, \emph{103}, 360--364.
\bibitem{Kovalenko98}
Kovalenko,~A.; Hirata,~F. Three-Dimensional Density Profiles of Water in
  Contact with a Solute of Arbitrary Shape: A {RISM} Approach. \emph{Chem.
  Phys. Lett.} \textbf{1998}, \emph{290}, 237--244.
\bibitem{Singer85}
Singer,~S.~J.; Chandler,~D. Free Energy Functions in the Extended {RISM}
  Approximation. \emph{Mol. Phys.} \textbf{1985}, \emph{55}, 621--625.
\bibitem{Kast08}
Kast,~S.~M.; Kloss,~T. Closed-Form Expressions of the Chemical Potential for
  Integral Equation Closures with Certain Bridge Functions. \emph{J. Chem.
  Phys.} \textbf{2008}, \emph{129}, 236101.
\bibitem{Fischer80}
Fischer,~J.; Methfessel,~M. Born--Green--Yvon Approach to the Local Densities
  of a Fluid at Interfaces. \emph{Phys. Rev. A} \textbf{1980}, \emph{22},
  2836--2843.
\bibitem{Griebel08}
Griebel,~M.; Jager,~L. The {BGY3dM} Model for the Approximation of Solvent
  Densities. \emph{J. Chem. Phys.} \textbf{2008}, \emph{129}, 174511.
\bibitem{Perkyns92}
Perkyns,~J.~S.; Pettitt,~B.~M. A Dielectrically Consistent Interaction Site
  Theory for Solvent--Electrolyte Mixtures. \emph{Chem. Phys. Lett.}
  \textbf{1992}, \emph{190}, 626--630.
\bibitem{Perkyns94}
Perkyns,~J.; Pettitt,~B.~M. Integral Equation Approaches to Structure and
  Thermodynamics of Aqueous Salt Solutions. \emph{Biophys. Chem.}
  \textbf{1994}, \emph{51}, 129--146.
\bibitem[Chiodo \latin{et~al.}(2007)Chiodo, Chuev, Erofeeva, Fedorov, Russo,
  and Sicilia]{Chiodo07}
Chiodo,~S.; Chuev,~G.~N.; Erofeeva,~S.~E.; Fedorov,~M.~V.; Russo,~N.;
  Sicilia,~E. Comparative Study of Electrostatic Solvent Response by {RISM} and
  {PCM} Methods. \emph{Int. J. Quantum Chem.} \textbf{2007}, \emph{107},
  265--274.
\bibitem{Chuev08}
Chuev,~G.~N.; Fedorov,~M.~V.; Chiodo,~S.; Russo,~N.; Sicilia,~E. Hydration of
  Ionic Species Studied by the Reference Interaction Site Model with a
  Repulsive Bridge Correction. \emph{J. Comput. Chem.} \textbf{2008},
  \emph{29}, 2406--2415.
\bibitem{Joung13}
Joung,~I.~S.; Luchko,~T.; Case,~D.~A. Simple Electrolyte Solutions: Comparison
  of {DRISM} and Molecular Dynamics Results for Alkali Halide Solutions.
  \emph{J. Chem. Phys.} \textbf{2013}, \emph{138}, 044103.
\bibitem{Makov95}
Makov,~G.; Payne,~M.~C. Periodic Boundary Conditions in \textit{ab initio}
  Calculations. \emph{Phys. Rev. B} \textbf{1995}, \emph{51}, 4014--4022.
\bibitem{Ng74}
Ng,~K.-C. Hypernetted Chain Solutions for the Classical One-Component Plasma up
  to {$\Gamma$}=7000. \emph{J. Chem. Phys.} \textbf{1974}, \emph{61},
  2680--2689.
\bibitem{Kovalenko00b}
Kovalenko,~A.; Hirata,~F. Potentials of Mean Force of Simple Ions in Ambient
  Aqueous Solution. {I}. {T}hree-Dimensional Reference Interaction Site Model
  Approach. \emph{J. Chem. Phys.} \textbf{2000}, \emph{112}, 10391--10402.
\bibitem{Kloss08b}
Kloss,~T.; Kast,~S.~M. Treatment of Charged Solutes in Three-Dimensional
  Integral Equation Theory. \emph{J. Chem. Phys.} \textbf{2008}, \emph{128},
  134505.
\bibitem[Perkyns \latin{et~al.}(2010)Perkyns, Lynch, Howard, and
  Pettitt]{Perkyns10}
Perkyns,~J.~S.; Lynch,~G.~C.; Howard,~J.~J.; Pettitt,~B.~M. Protein Solvation
  from Theory and Simulation: Exact Treatment of Coulomb Interactions in
  Three-Dimensional Theories. \emph{J. Chem. Phys.} \textbf{2010}, \emph{132},
  064106.
\bibitem{Heil15}
Heil,~J.; Kast,~S.~M. {3D RISM} Theory with Fast Reciprocal-Space
  Electrostatics. \emph{J. Chem. Phys.} \textbf{2015}, \emph{142}, 114107.
\bibitem{Tenno93}
Ten-no,~S.; Hirata,~F.; Kato,~S. A Hybrid Approach for the Solvent Effect on
  the Electronic Structure of a Solute Based on the {RISM} and
  {H}artree--{F}ock Equations. \emph{Chem. Phys. Lett.} \textbf{1993},
  \emph{214}, 391--396.
\bibitem{Tenno94}
Ten-no,~S.; Hirata,~F.; Kato,~S. Reference Interaction Site Model
  Self-Consistent Field Study for Solvation Effect on Carbonyl Compounds in
  Aqueous Solution. \emph{J. Chem. Phys.} \textbf{1994}, \emph{100},
  7443--7453.
\bibitem{Kovalenko99}
Kovalenko,~A.; Hirata,~F. Self-Consistent Description of a Metal--Water
  Interface by the {K}ohn--{S}ham Density Functional Theory and the
  Three-Dimensional Reference Interaction Site Model. \emph{J. Chem. Phys.}
  \textbf{1999}, \emph{110}, 10095--10112.
\bibitem{Kloss08}
Kloss,~T.; Heil,~J.; Kast,~S.~M. Quantum Chemistry in Solution by Combining
  {3D} Integral Equation Theory with a Cluster Embedding Approach. \emph{J.
  Phys. Chem. B} \textbf{2008}, \emph{112}, 4337--4343.
\bibitem{Gusarov06}
Gusarov,~S.; Ziegler,~T.; Kovalenko,~A. Self-Consistent Combination of the
  Three-Dimensional {RISM} Theory of Molecular Solvation with Analytical
  Gradients and the {A}msterdam Density Functional Package. \emph{J. Phys.
  Chem. A} \textbf{2006}, \emph{110}, 6083--6090.
\bibitem{Sato13}
Sato,~H. A Modern Solvation Theory: Quantum Chemistry and Statistical
  Chemistry. \emph{Phys. Chem. Chem. Phys.} \textbf{2013}, \emph{15},
  7450--7465.
\bibitem{Bo15}
Li,~B.; Matveev,~A.~V.; Kr\"uger,~S.; R\"osch,~N. Uranyl Solvation by a
  Reference Interaction Site Model. \emph{Comput. Theor. Chem.} \textbf{2015},
  \emph{1051}, 151--160.
\bibitem{Leeuwen59}
van Leeuwen,~J.; Groeneveld,~J.; de~Boer,~J. New Method for the Calculation of
  the Pair Correlation Function. {I}. \emph{Physica} \textbf{1959}, \emph{25},
  792--808.
\bibitem{Berendsen87}
Berendsen,~H. J.~C.; Grigera,~J.~R.; Straatsma,~T.~P. The Missing Term in
  Effective Pair Potentials. \emph{J. Phys. Chem.} \textbf{1987}, \emph{91},
  6269--6271.
\bibitem{Mahoney00}
Mahoney,~M.~W.; Jorgensen,~W.~L. A Five-Site Model for Liquid Water and the
  Reproduction of the Density Anomaly by Rigid, Nonpolarizable Potential
  Functions. \emph{J. Chem. Phys.} \textbf{2000}, \emph{112}, 8910--8922.
\bibitem{Bridgeman64}
Bridgeman,~O.~C.; Aldrich,~E. Vapor Pressure Tables for Water. \emph{J. Heat
  Transfer} \textbf{1964}, \emph{86}, 279--286, by way of NIST Chemistry
  Webbook, \url{http://webbook.nist.gov/chemistry/}.
\bibitem{petsc-user-ref}
Balay,~S.; Adams,~M.~F.; Brown,~J.; Brune,~P.; Buschelman,~K.; Eijkhout,~V.;
  Gropp,~W.~D.; Kaushik,~D.; Knepley,~M.~G.; McInnes,~L.~C. \latin{et~al.}
  {PETS}c Users Manual. 2013.
\bibitem{Cummings81}
Cummings,~P.~T.; Stell,~G. Exact Asymptotic Form of the Site-Site Direct
  Correlation Function for Rigid Polar Molecules. \emph{Mol. Phys.}
  \textbf{1981}, \emph{44}, 529--531.
\bibitem{FFTW05}
Frigo,~M.; Johnson,~S.~G. The Design and Implementation of {FFTW3}.
  \emph{Proceedings of the IEEE} \textbf{2005}, \emph{93}, 216--231.
\bibitem{Pettitt82}
Pettitt,~B.~M.; Rossky,~P.~J. Integral Equation Predictions of Liquid State
  Structure for Waterlike Intermolecular Potentials. \emph{J. Chem. Phys.}
  \textbf{1982}, \emph{77}, 1451--1457.
\bibitem{Luchko10}
Luchko,~T.; Gusarov,~S.; Roe,~D.~R.; Simmerling,~C.; Case,~D.~A.;
  Tuszynski,~J.; Kovalenko,~A. Three-Dimensional Molecular Theory of Solvation
  Coupled with Molecular Dynamics in {Amber}. \emph{J. Chem. Theory Comput.}
  \textbf{2010}, \emph{6}, 607--624.
\bibitem{Dunlap90}
Dunlap,~B.~I.; R\"{o}sch,~N. In \emph{Density Functional Theory of Many-Fermion
  Systems}; Trickey,~S.~B., Ed.; Advances in Quantum Chemistry; Academic Press,
  1990; Vol.~21; pp 317--399.
\bibitem{ParaGaussV3.2}
R\"{o}sch,~N. \latin{et~al.}  {\textsc{ParaGauss}}, Version 4.0, Technische Universit\"{a}t
  M\"{u}nchen, 2014.
\bibitem{Matveev08}
Matveev,~A.~V.; R\"{o}sch,~N. Atomic Approximation to the Projection on
  Electronic States in the {D}ouglas--{K}roll--{H}ess Approach to the
  Relativistic {K}ohn--{S}ham Method. \emph{J. Chem. Phys.} \textbf{2008},
  \emph{128}, 244102.
\bibitem{rev:roesch96}
{R{\"o}sch},~N.; {Kr{\"u}ger},~S.; Mayer,~M.; Nasluzov,~V.~A. In \emph{Recent
  Developments and Applications of Modern Density Functional Theory};
  Seminario,~J.~M., Ed.; Theoretical and Computational Chemistry Series;
  Elsevier: Amsterdam, 1996; Vol.~4; p 497.
\bibitem{Goerling99}
G\"orling,~A.; Trickey,~S.; Gisdakis,~P.; R\"osch,~N. In \emph{Organometallic
  Bonding and Reactivity}; Brown,~J., Hofmann,~P., Eds.; Topics in
  Organometallic Chemistry; Springer Berlin Heidelberg, 1999; Vol.~4; pp
  109--163.
\bibitem{kochDFT}
Koch,~W.; Holthausen,~M.~C. \emph{A Chemist's Guide to Density Functional
  Theory}; Wiley-VCH: Weinheim, 2001.
\bibitem{Becke88}
Becke,~A.~D. Density-Functional Exchange-Energy Approximation with correct
  asymptotic behavior. \emph{Phys. Rev. A} \textbf{1988}, \emph{38},
  3098--3100.
\bibitem{Perdew86c}
Perdew,~J.~P. Density-Functional Approximation for the Correlation Energy of
  the Inhomogeneous Electron Gas. \emph{Phys. Rev. B} \textbf{1986}, \emph{33},
  8822.
\bibitem{Moskaleva06b}
Moskaleva,~L.~V.; Matveev,~A.~V.; Dengler,~J.; R\"{o}sch,~N. The Heat of
  Formation of Gaseous {PuO}$_2^{2+}$ from Relativistic Density Functional
  Calculations. \emph{Phys. Chem. Chem. Phys.} \textbf{2006}, \emph{8},
  3767--3773.
\bibitem{Moskaleva06a}
Moskaleva,~L.~V.; Matveev,~A.~V.; Kr\"{u}ger,~S.; R\"{o}sch,~N. The Heat of
  Formation of the Uranyl Dication: Theoretical Evaluation Based on
  Relativistic Density Functional Calculations. \emph{Chem. Eur. J.}
  \textbf{2006}, \emph{12}, 629--634.
\bibitem{Kremleva12b}
Kremleva,~A.; Zhang,~Y.; Shor,~A.~M.; Kr\"uger,~S.; Joseph,~C.; Raditzky,~B.;
  Schmeide,~K.; Sachs,~S.; Bernhard,~G.; R\"osch,~N. Uranyl({VI}) Complexation
  by Sulfonate Ligands: A Relativistic Density Functional and Time-Resolved
  Laser-Induced Fluorescence Spectroscopy Study. \emph{Eur. J. Inorg. Chem.}
  \textbf{2012}, \emph{2012}, 3636--3644.
\bibitem{Bondi64}
Bondi,~A. van der {W}aals Volumes and Radii. \emph{J. Phys. Chem.}
  \textbf{1964}, \emph{68}, 441--451.
\bibitem{Su09}
Su,~P.; Li,~H. Continuous and Smooth Potential Energy Surface for Conductorlike
  Screening Solvation Model Using Fixed Points with Variable Areas. \emph{J.
  Chem. Phys.} \textbf{2009}, \emph{130}, 074109.
\bibitem{Chaffey-Millar11}
Chaffey-Millar,~H.; Nikodem,~A.; Matveev,~A.~V.; Kr\"{u}ger,~S.; R\"{o}sch,~N.
  Improving Upon String Methods for Transition State Discovery. \emph{J. Chem.
  Theory Comput.} \textbf{2012}, \emph{8}, 777--786.
\bibitem{Nikodem13}
Nikodem,~A.; Matveev,~A.~V.; Zheng,~B.-X.; R\"{o}sch,~N. Efficient Two-Step
  Procedures for Locating Transition States of Surface Reactions. \emph{J.
  Chem. Theory Comput.} \textbf{2013}, \emph{9}, 588--599.
\bibitem{Sergiievskyi14}
Sergiievskyi,~V.~P.; Jeanmairet,~G.; Levesque,~M.; Borgis,~D. Fast Computation
  of Solvation Free Energies with Molecular Density Functional Theory:
  Thermodynamic-Ensemble Partial Molar Volume Corrections. \emph{J. Phys. Chem.
  Lett.} \textbf{2014}, \emph{5}, 1935--1942.
\bibitem{Joung08}
Joung,~I.~S.; Cheatham,~T.~E. Determination of Alkali and Halide Monovalent Ion
  Parameters for Use in Explicitly Solvated Biomolecular Simulations. \emph{J.
  Phys. Chem. B} \textbf{2008}, \emph{112}, 9020--9041.
\bibitem{Schmid00}
Schmid,~R.; Miah,~A.~M.; Sapunov,~V.~N. A New Table of the Thermodynamic
  Quantities of Ionic Hydration: Values and Some Applications (Enthalpy-Entropy
  Compensation and {B}orn Radii). \emph{Phys. Chem. Chem. Phys.} \textbf{2000},
  \emph{2}, 97--102.
\bibitem{Gibson05}
Gibson,~J.~K.; Haire,~R.~G.; Santos,~M.; Mar\c{c}alo,~J.; Pires~de Matos,~A.
  Oxidation Studies of Dipositive Actinide Ions, {An}$^{2+}$ ({An} = {Th}, {U},
  {Np}, {Pu}, {Am}) in the Gas Phase: Synthesis and Characterization of the
  Isolated Uranyl, Neptunyl, and Plutonyl Ions {UO}$_2^{2+}$(g),
  {NpO}$_2^{2+}$(g), and {PuO}$_2^{2+}$(g). \emph{J. Phys. Chem. A}
  \textbf{2005}, \emph{109}, 2768--2781.
\bibitem{Farkas00}
Farkas,~I.; B\'{a}nyai,~I.; Szab\'{o},~Z.; Wahlgren,~U.; Grenthe,~I. Rates and
  Mechanisms of Water Exchange of {UO}$_2^{2+}$(aq) and
  {UO}$_2$(oxalate){F}({H}$_2${O})$^{2-}$: A Variable-Temperature $^{17}${O}
  and $^{19}${F} {NMR} Study. \emph{Inorg. Chem.} \textbf{2000}, \emph{39},
  799--805.
\bibitem{Vallet01}
Vallet,~V.; Wahlgren,~U.; Schimmelpfennig,~B.; Szab\'{o},~Z.; Grenthe,~I. The
  Mechanism for Water Exchange in [{UO}$_2$({H}$_2${O})$_5$]$^{2+}$ and
  [{UO}$_2$(oxalate)$_2$({H}$_2${O})]$^{2-}$, as Studied by Quantum Chemical
  Methods. \emph{J. Am. Chem. Soc.} \textbf{2001}, \emph{123},
  11999--12008.
\bibitem{Kerisit10}
Kerisit,~S.; Liu,~C. Molecular Simulation of the Diffusion of Uranyl Carbonate
  Species in Aqueous Solution. \emph{Geochim. Cosmochim. Acta} \textbf{2010},
  \emph{74}, 4937--4952.
\bibitem{Denning76}
Denning,~R.; Snellgrove,~T.; Woodwark,~D. The Electronic Structure of the
  Uranyl Ion. \emph{Mol. Phys.} \textbf{1976}, \emph{32}, 419--442.
\bibitem{Denning79}
Denning,~R.; Foster,~D.; Snellgrove,~T.; Woodwark,~D. The Electronic Structure
  of the Uranyl Ion. \emph{Mol. Phys.} \textbf{1979}, \emph{37},
  1089--1107.
\bibitem{Toth81}
Toth,~L.~M.; Begun,~G.~M. Raman Spectra of Uranyl Ion and its Hydrolysis
  Products in Aqueous Nitric Acid. \emph{J. Phys. Chem.} \textbf{1981},
  \emph{85}, 547--549.
\bibitem{Gal92}
G\'al,~M.; Goggin,~P.; Mink,~J. Vibrational Spectroscopic Studies of Uranyl
  Complexes in Aqueous and Non-Aqueous Solutions. \emph{Spectrochim. Acta, Part
  A} \textbf{1992}, \emph{48}, 121 -- 132.
\bibitem{Ramakrishnan11}
Ramakrishnan,~R.; Matveev,~A.~V.; R\"osch,~N. Effects of the Self-Interaction
  Error in {K}ohn--{S}ham Calculations: A {DFT+U} Case Study on Penta-Aqua
  Uranyl({VI}). \emph{Comput. Theor. Chem.} \textbf{2011}, \emph{963},
  337--343.
\bibitem{Jackson08}
Jackson,~V.~E.; Craciun,~R.; Dixon,~D.~A.; Peterson,~K.~A.; de~Jong,~W.~A.
  Prediction of Vibrational Frequencies of {UO}$_2^{2+}$ at the {CCSD(T)}
  Level. \emph{J. Phys. Chem. A} \textbf{2008}, \emph{112}, 4095--4099.
\bibitem{Tsushima07}
Tsushima,~S. Hydration and Water-Exchange Mechanism of the {UO}$_2^{2+}$ Ion
  Revisited: The Validity of the "$n + 1$" Model. \emph{J. Phys. Chem. A}
  \textbf{2007}, \emph{111}, 3613--3617.
\bibitem{Buehl06b}
B\"{u}hl,~M.; Kabrede,~H. Mechanism of Water Exchange in Aqueous Uranyl({VI})
  Ion. A Density Functional Molecular Dynamics Study. \emph{Inorg. Chem.}
  \textbf{2006}, \emph{45}, 3834--3836.
\bibitem{Rotzinger07}
Rotzinger,~F.~P. The Water-Exchange Mechanism of the
  [{UO}$_2$({OH}$_2$)$_5$]$^{2+}$ Ion Revisited: The Importance of a Proper
  Treatment of Electron Correlation. \emph{Chem. Eur. J.} \textbf{2007},
  \emph{13}, 800--811.
\end{thebibliography}
